### 2023-11-08 manuscript/additional_files.Rmd
Move table S6 back into the main manuscript as table 3

Additional file 3.pdf - Supplementary tables -
Supplementary tables S2, S3, S4, S5, S6 showing adduct, isotopic, transformation, R package benchmarking information and a summary of the molecular formula assignment results for the example sample matrices respectively.

Additional file 4.csv - Table S7 -
The molecular formula assignments for *m/z* across all experimental matrices along with any match KEGG compound IDs.

Additional file 5.csv Table S8 -
The *m/z* features directly matched to predicted ionisation products of the spiked chemical compounds in urine.

Additional file 6.csv Table S9 -
The *m/z* features assigned to spiked chemical compounds in urine.

>>>>

Additional file 3.pdf - Supplementary tables -
Supplementary tables S2, S3, S4, S5, showing adduct, isotopic, transformation and R package benchmarking information respectively.

Additional file 4.csv Table S6 -
The *m/z* features directly matched to theoretical ionisation products of the chemical standards in the standards mixed and spiked urine.

Additional file 5.csv Table S7 -
The *m/z* features assigned to chemical standards in the standards mix and spiked urine.

Additional file 6.csv - Table S8 -
The molecular formula assignments for *m/z* across all experimental matrices along with any match KEGG compound IDs.

### 2023-11-08 manuscript/manuscript.Rmd
Move table S6 back into the main manuscript as table 3

An overview of the molecular formula assignments made across the example sample matrices is provided in Table S6 (Additional file 3).
All of the assignments for these example matrices along with any matched KEGG compound IDs are provided in Additional file 6.
The assignments obtained from the *B. distachyon* is provided as an example showing the intended real world application of the molecular formula assignment approach to a sample set that includes multiple underlying experimental classes in the correlation network.
A similar number of molecular formulas were assigned to the FIE-HRMS matrices for the spiked human urine and *B. distachyon* matrices as well as similar numbers of molecular formulas that were matched to KEGG compounds.

@@

>>>>

An overview of the molecular formula assignments made across the example sample matrices is provided in Table \@ref(tab:assignment-results).
All of the assignments for these example matrices along with any matched KEGG compound IDs are provided in Additional file 6.
The assignments obtained from the *B. distachyon* is provided as an example showing the intended real world application of the molecular formula assignment approach to a sample set that includes multiple underlying experimental classes in the correlation network.
A similar number of molecular formulas were assigned to the FIE-HRMS matrices for the spiked human urine and *B. distachyon* matrices as well as similar numbers of molecular formulas that were matched to KEGG compounds.

@@

```{r assignment-results}
tar_read(assignment_results) %>%
  dplyr::full_join(
    tar_read(assignment_matches) %>% 
      dplyr::mutate(
        matrix = matrix %>% 
          replace(
            matrix == 'standards',
            'standards-mix'
          )
      ), 
    by = c("matrix", "technique")) %>% 
  mutate(
    matrix = paste(matrix,technique)
  ) %>%
  mutate(
    n_assignments = glue::glue(
      '{n_assignments} ({signif(n_assignments/n_features * 100,digits = 3)}\\%)'),
    across(where(is.numeric),~prettyNum(.x,big.mark = ','))) %>%
  select(-technique) %>% 
  dplyr::rename(
    `\\textit{m/z} features` = n_features,
    correlations = n_correlations,
    relationships = n_relationships,
    `adduct and isotopic step assignments` = n_ai_assignments,
    `transformation step assignments` = n_t_assignments,
    `assigned \\textit{m/z}` = n_assignments,
    `molecular formulas (MF)` = n_MFs,
    `KEGG compound matches` = KEGG_compound_matches,
    `KEGG MF matches` = KEGG_MF_matches,
    `matched chemical standards` = matched_standards) %>% 
  tidyr::gather(Variable,Value,-matrix) %>% 
  mutate(
    Value = replace(Value,
                    Value == 'NA',
                    'N/A')) %>% 
  tidyr::spread(matrix,Value) %>% 
  slice(c(1,4,9,2,10,3,8,6,5)) %>%
  dplyr::select(
    Variable,
    `standards-mix FIE-HRMS`,
    `spiked-urine FIE-HRMS`,
    `brachy FIE-HRMS`,
    `brachy C18-UHPLC-HRMS`
  ) %>% 
  set_colnames(
    stringr::str_split_fixed(colnames(.),
                             ' ',2)[,2]) %>% 
  knitr::kable(
    format = 'latex',
    booktabs = TRUE,
    linesep = '',
    escape = FALSE,
    align = c(
      rep('l',1),
      rep('r',4)
    ),
    caption = 'A summary of the molecular formula assignment results for the example sample matrices.') %>%
  kable_styling(
    font_size = 10,
    latex_options = "HOLD_position"
  ) %>%
  add_header_above(c(
    " ",
    "Standards mix" = 1,
    "Human urine" = 1,
    "\\\\textit{B. distachyon} leaf" = 2),
    escape = FALSE)
```
